Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-29 docs/ms.tex
Update ms.tex

The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually 10 times smaller than the intrinsic shape 
noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
The main source of uncertainty of tangential shear comes from the intrinsic shape "noise" . We know little knowledge about 
the distribution of intrinsic ellipticity,exception the assumption that the orientational angle should be isotropic.
With this assumption,we can use the average of galaxies' ellipticity as an estimator of tangential shear.--However by 
doing this we lose some information about how the ellipticity are distributed. Simple average point estimator can't 
use the other reasonable assumption about intrinsic shape distribution --galaxies in different sky patches should have 
the same shape distibution--which is the result of homogeneous Universe.

>>>>

The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually more than 10 times smaller than the intrinsic shape 
noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
The main source of uncertainty of tangential shear comes from the intrinsic shape "noise" . We know little knowledge about 
the distribution of intrinsic ellipticity,exception the assumption that the orientational angle should be isotropic.
With this assumption,we can use the average of galaxies' ellipticity as an estimator of tangential shear.--However by 
doing this we lose some information about how the ellipticity are distributed. Simple average point estimator can't 
use the other reasonable assumption about intrinsic shape distribution --galaxies in different sky patches should have 
the same shape distibution--which is the result of homogeneous Universe.
